The Error Estimate of Force Calculation in the Inhomogeneous Molecular Systems

### 2011-12-16 shortRange.inhomo/alltext/pubilsh/letter.to.referee/letter.tex
add letter.to.referee and graphical.abstract

\documentclass{letter}

\usepackage{graphicx}

\renewcommand{\baselinestretch}{1.0}
% \setlength{\footskip}{0cm}
%\addtolength{\textheight}{10cm}
% \sloppy

\address{Institute for Mathematics \\
  Freie Universit\"at Berlin\\
  Arnimallee 6\\
  14195 Berlin, Germany 
}
\signature{Han Wang}

% \def\urltilda{\kern -.15em\lower .7ex\hbox{\~{}}\kern .04em}
% \def\urlunder{\lower .1ex\hbox{\_{}}\kern .04em}
% \def\urldot{\kern -.10em.\kern -.10em}
% \def\urlhttp{http\kern -.10em\lower -.1ex\hbox{:}\kern -.12em\lower 0ex\hbox{/}\kern -.18em\lower 0ex\hbox{/}}
% \parindent0ex

\begin{document}

\begin{letter}{
    The Referees of\\
    Physical Chemistry Chemical Physics\\
    \vskip 1cm
  }
% \begin{picture}(0,0)
%   \put(-30,22){
%     \parbox{0.25\textwidth}{
% %	\includegraphics[scale=0.4]{logo-icp-notext.pdf}
%     }
%   }
%   \put(264,10){
%     \parbox{0.25\textwidth}{
% 	\includegraphics[scale=0.28]{Fub-logo.eps}
%     }
%   }
% \end{picture}

\opening{Dear Referees,\vskip .5cm}
Hereby we would like to submit our article:\\

@@

Most of previous error estimates in this field assumed the homogeneity
of the system. As far as we know, the present work for the first time
proposed an error estimate for the short-range interactions in the
inhomogeneous molecular systems, presenting new phenomena that do not
happen in the homogeneous systems.  We showed that the adaptive cut-off
and the force correction methods greatly improve the efficiency and
accuracy, and successfully avoid the problem of the standard cut-off
method, so they should be of special interest for
understanding the inhomogeneous molecular systems, and for
designing high
performance molecular simulation softwares.
\\
\vskip 3cm

\closing{Best regards,}
  % \put(-85,-50){\includegraphics[scale=0.2]{zhang-signature.pdf}}
% }

>>>>

\documentclass{scrlttr2}
\usepackage{graphicx}
\usepackage{hyperref}
% provides a justified text without hyphenation
\usepackage[none]{hyphenat}
\renewcommand{\baselinestretch}{1.0}
\setlength{\footskip}{0cm}
%\addtolength{\textheight}{10cm}
\sloppy

\KOMAoptions{foldmarks=false,fromalign=left,fromrule=true,fromlogo=false,backaddress=false}
\setkomavar{fromname}{Dr. Han Wang}
\setkomavar{fromaddress}
{Department of Mathematics \& Computer Science \\
  Freie Universit\"at Berlin\\
  Arnimallee 6\\
  14195 Berlin, Germany 
}

\def\urltilda{\kern -.15em\lower .7ex\hbox{\~{}}\kern .04em}
\def\urlunder{\lower .1ex\hbox{\_{}}\kern .04em}
\def\urldot{\kern -.10em.\kern -.10em}
\def\urlhttp{http\kern -.10em\lower -.1ex\hbox{:}\kern -.12em\lower 0ex\hbox{/}\kern -.18em\lower 0ex\hbox{/}}
\parindent0ex

\begin{document}
\makeatletter
\@setplength{toaddrvpos}{6em}
\@setplength{sigbeforevskip}{0.5em}
\@setplength{sigindent}{0em}
\@setplength{refvpos}{35ex}

\begin{letter}{
    The Referees of\\
    Physical Chemistry Chemical Physics\\
    \vskip 0cm
  }
\begin{picture}(0,0)
  \put(-30,22){
    \parbox{0.25\textwidth}{
%	\includegraphics[scale=0.4]{logo-icp-notext.pdf}
    }
  }
  \put(264,10){
    \parbox{0.25\textwidth}{
	\includegraphics[scale=0.28]{Fub-logo.pdf}
    }
  }
\end{picture}

\opening{Dear Referees,}
Hereby we would like to submit our article:\\

@@

Most of previous error estimates in this field assumed the homogeneity
of the system. As far as we know, the present work for the first time
proposed an error estimate for the short-range interactions in the
inhomogeneous molecular systems, presenting new phenomena that do not
happen in the homogeneous systems.  We shew that the adaptive cut-off
and the force correction methods greatly improve the efficiency and
accuracy, and successfully avoid the problem of the standard cut-off
method, so they should be of special interest for designing high
performance molecular simulation software.
\\

\closing{Best regards,
  % \put(-85,-50){\includegraphics[scale=0.2]{zhang-signature.pdf}}
}

% \newpage

% \parindent0ex \textbf{Corresponding author}:\\

% \qquad Pingwen Zhang

% \qquad LMAM and School of Mathematical Sciences

% \qquad Peking University

% \qquad 100871 Beijing, P.R. China

% \qquad Phone: +86-10-62759851

% \qquad Fax: +86-10-62751801

% \qquad \href{mailto:pzhang@pku.edu.cn}{\tt pzhang@pku.edu.cn} \\

% \parindent0ex\textbf{Referees}:\\
% Furthermore as knowledgeable referees in this field we suggest:
% \begin{itemize}
% \item Christoph Dellago \\
%   Faculty of Physics\\
%   University of Vienna\\
%   Boltzmanngasse 5 (1st floor, room 3105) \\
%   1090 Vienna\\
%   Austria\\
%   \href{mailto:Christoph.Dellago@univie.ac.at}{\tt Christoph.Dellago@univie.ac.at}
% \item Giovanni Ciccotti \\
%   Department of Physics \\
%   University of Roma "La Sapienza"\\
%   P.le Aldo Moro 5\\
%   00185 Roma\\
%   Italy\\
%   \href{mailto:giovanni.ciccotti@phys.uniroma1.it}{\tt giovanni.ciccotti@phys.uniroma1.it}
% \item Daan Frenkel\\
%   Cambridge University Centre for Computational Chemistry\\
%   Department of Chemistry\\
%   Lensfield Road\\
%   Cambridge CB2 1EW\\
%   United Kindom\\
%   \href{mailto:df246@cam.ac.uk}{\tt df246@cam.ac.uk}
% \item Kurt Binder\\
%   KOMET 331 \\
%   Institute of Physics\\
%   Johannes Gutenberg University Mainz \\
%   D 55099 Mainz \\
%   Germany\\
%   \href{mailto:kurt.binder@uni-mainz.de}{\tt kurt.binder@uni-mainz.de}
% \end{itemize}

% \parindent0ex\textbf{Color figures}:
% \begin{itemize}
%   \item[] A main aspect of the article is accuracy, therefore even smallest
%     deviations should be recognizable in the plots. Though we already used
%     different line styles, coloring is inevitable to distinguish the various
%     amount of information correctly. Therefore we regard colored versions of
%     Figure 1 and 2 as essential to provide a clear picture for the reader.
% \end{itemize}
